\papertitle

### 2021-03-12 source_separation/paper/paper.tex
Add plot with avg and stddev
Capitalize headings
Add to future work

			\subsubsection{Music source separation}
			\textbf{Open-Unmix}\\
			Open-Unmix~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich2017}. It is actually composed of multiple models that are trained for each instrumental target. Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectional LSTM network. Open-Unmix operates on the Short Time Fourier Transform (STFT) of the input mixture, which is first standardized. It predicts the target by multiplying the output of the LSTM network with the magnitude spectrogram of the input, essentially applying a mask. Open-Unmix also uses Wiener filtering as a last processing step.

@@

			\subsubsection{Universal sound separation}
			\textbf{Non-negative Matrix Factorization}\\
			Non-negative matrix factorization \cite{Cichocki_NMF} \cite{Fevotte_NMF} is an \`a priori method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

@@

@@

>>>>

			\subsubsection{Music Source Separation}
			\textbf{Open-Unmix}\\
			Open-Unmix~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich2017}. It is actually composed of multiple models that are trained for each instrumental target. Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectional LSTM network. Open-Unmix operates on the Short Time Fourier Transform (STFT) of the input mixture, which is first standardized. It predicts the target by multiplying the output of the LSTM network with the magnitude spectrogram of the input, essentially applying a mask. Open-Unmix also uses Wiener filtering as a last processing step.

@@

			\subsubsection{Universal Sound Separation}
			\textbf{Non-negative Matrix Factorization}\\
			Non-negative matrix factorization \cite{Cichocki_NMF} \cite{Fevotte_NMF} is an \`a priori method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

@@

	\begin{figure}[t]
		\centering
			\includegraphics[width=\columnwidth]{figures/graph.png}
			\caption{Plot showing the average distance and standard deviation between target and solution for each orchestration method.}\label{fig:plot}
	\end{figure}

@@

		As we stated in Section \ref{sec:introduction}, we chose static orchestration instead of dynamic orchestration to avoid entangling the problems of time segmentation and source separation. Future work could include applying source separation to dynamic targets and performing dynamic orchestration.
